Pool Model

### 2025-08-28 pool_model.tex
formatting
simplify caption; move to main text

        Darker colours indicate less present nutrients.

@@

        \includegraphics[width=0.9\columnwidth]{Figures/abm-homogenous/abm_ode_comparison.png}
        \subcaption{Homogenous initial cell distribution, $D=30.0$\unit{\micro\metre\squared\per\minute}}
        \includegraphics[width=0.9\columnwidth]{Figures/abm-homogenous-low-diffusion/abm_ode_comparison.png}
        \subcaption{Homogenous initial cell distribution, $D=5.0$\unit{\micro\metre\squared\per\minute}}
        \includegraphics[width=0.9\columnwidth]{Figures/abm-inhomogenous/abm_ode_comparison.png}%
        \subcaption{Heterogeneous initial cell distribution, $D=30.0$\unit{\micro\metre\squared\per\minute}}
        \includegraphics[width=0.9\columnwidth]{Figures/abm-random/abm_ode_comparison.png}%
        \subcaption{Randomized initial cell distribution, $D=5.0$\unit{\micro\metre\squared\per\minute}}
        The diffusion constants are chosen $D_R=D_I=D$.

@@

>>>>

        Darker colours indicate that less nutrients are present.

@@

@@

        \includegraphics[width=\columnwidth]{Figures/abm-homogenous/abm_ode_comparison.png}
        \subcaption{Homogenous distribution, $D=30.0$\unit{\micro\metre\squared\per\minute}}
        \includegraphics[width=\columnwidth]{Figures/abm-homogenous-low-diffusion/abm_ode_comparison.png}
        \subcaption{Homogenous distribution, $D=5.0$\unit{\micro\metre\squared\per\minute}}
        \includegraphics[width=\columnwidth]{Figures/abm-inhomogenous/abm_ode_comparison.png}%
        \subcaption{Heterogeneous distribution, $D=30.0$\unit{\micro\metre\squared\per\minute}}
        \includegraphics[width=\columnwidth]{Figures/abm-random/abm_ode_comparison.png}%
        \subcaption{Randomized distribution, $D=5.0$\unit{\micro\metre\squared\per\minute}}
        The diffusion constants are chosen such that $D_R=D_I=D$.
